Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-12 Text/introduction.tex
Started doing the Peclet number simulations. Need to find applicable regime.

\section{Keeping Peclet}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well.

We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.

>>>>

\section{Keeping Peclet}
This section addresses the performance of the simulations. The ulimate goal is to increase
velocity at least by several orders while keeping dimensionless parameters the same. Increasing
velocity can result in simulations of a lot of unit cells required for continuous picture
representation.

Only nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. The runs were made with
velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
boundary conditions were used and mass transfer coefficient was calculated according to Eq.
(\ref{main:simulation:equation}).
\begin{table}[htb!]
\begin{tabularx}{0.5\textwidth}{|X|X|}
\hline
$U_{bubble}$& $Ca$\\
\hline
0.0055&0.097\\
0.0143&0.254\\
0.0297&0.526\\
0.0424&0.750\\
0.0588&1.040\\
\hline
\end{tabularx}
\end{table}
For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
thumb that for such simulations the velocity shouldn't be more than $0.05$.

\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
\caption{The same Peclet number for $Ca=0.0055$. One can see that
the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
concentration!!!} \label{fig:ca0055:keeping:peclet}}
\end{figure}
